Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra

### 2024-08-26 paper/main.tex
update color palette and data png
use color-blind palette; update images

\title{Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra}
\author{Stephen A. Walsh\thanks{Corresponding author: Division of Natural Sciences, 
        Math and Technology, Elms College, {\tt walshst@elms.edu}} \and 
        Annie S. Booth\thanks{Department of Statistics, North Carolina State University} \and
        David Higdon\thanks{Department of Statistics, Virginia Tech} \and
        Marco A.R. Ferreira\footnotemark[3]}
\date{\today}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_data.png}
    \caption{The perturbation theory, low resolution runs, and high resolution run for the first training cosmology. The weighted average is also shown as a dashed line. Dotted lines at the bottom indicate where each data type is deemed approximately unbiased.}
    \label{fig:plot_data}
\end{figure}

@@

priors here

@@

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{rmse_by_k.png}
    \caption{Average RMSE of each method across all $k$ values.}
    \label{fig:plot_rmse_k}
\end{figure}

@@

>>>>

\title{Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra}
\author{Stephen A. Walsh\thanks{Corresponding author: Division of Natural Sciences, 
        Math and Technology, Elms College, {\tt walshst@elms.edu}} \and 
        Annie S. Booth\thanks{Department of Statistics, North Carolina State University} \and
        David Higdon\thanks{Department of Statistics, Virginia Tech} \and
        Marco A.R. Ferreira\footnotemark[3] \and
        Kelly Moran\thanks{Los Alamos National Laboratory} \and
        Katrin Heitmann\thanks{Argonne National Laboratory}}
\date{\today}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_data.png}
    \caption{Left: The perturbation theory, low resolution runs, and high resolution run for the first training cosmology. The weighted average is also shown as a dashed line. Dotted lines at the bottom indicate where each data type is deemed approximately unbiased. Right: The same image, but only where the low resolution runs are approximately unbiased.}
    \label{fig:plot_data}
\end{figure}

@@

\textcolor{blue}{Annie, please put the newest prior specs here.}

@@

\subsection{CAMB Data}
\label{subsec:camb}

Here, we look over the CAMB data to see how our method performs.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{rmse_by_k.png}
    \caption{Left: Average RMSE of each prediction method across all $k$ values. Right: Average RMSE for each method when using the held-out computer model runs to train the model. In each case, the truth is assumed to be the weighted average of the computer model runs.}
    \label{fig:plot_rmse_k}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{pred_1to6.png}
    \caption{Results of all six predictions for both methods on the held-out cosmologies (weighted average subtracted). CosmicEMU is dashed, DGP.HM is dotted, and solid gray lines show results of held-out computer model runs.}
    \label{fig:plot_pred_1to6}
\end{figure}
